An Automatic Verification Framework for Software Configurations

### 2016-05-07 OSDI/arch.tex
config: more update

We propose \app, an automatic verification framework,
which can solve configuration errors, \eg, ordering errors
and fine-grained value correlation, that previous work cannot tackle.
As depicted in Figure~\ref{fig-overview}, \app has three main steps:
translation, learning and checking. In this section, we briefly
describe how does each step work.

\para{Initial state.}
We start
with the assumption that we are given a number of (not necessarily) 
correct configuration files belonging to the same system, 
such as MySQL or Apache. 
Such files follow similar patterns, which we exploit
in a learning algorithm to build rules that
describe a language model for the files.

\para{Translator.}
The translator component first parses the input sample 
dataset (containing both configuration files and system environment
information), and then transforms them to a more structured
and typed intermediate representation.
When we run type inference on a configuration file, 
the type of a variable cannot always be fully determined from 
a single value.
We address this problem 
by introducing so called {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types with their probability distributions. 
We can later use these more structured files
as a training set to learn the rules.

@@

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which needs users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class is looked as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.

Although the learner does necessarily rely on templates,
\app still offers a template DB, which will be used to offer
execution environment related information.
It is widely known that any existing learning algorithm cannot
derive rules checking environment violation, \eg,
whether current account is the owner of a certain path.
In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment related configuration errors.

>>>>

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can solve many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors 
and fine-grained value correlation) that previous efforts cannot 
detect. As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning and checking. In this section, we briefly
describe how does each step work.

\para{Initial phase.}
We start with the assumption 
that we are given a number of (not necessarily correct) 
configuration files belonging to the same system, 
such as MySQL or Apache. 
These given files follow similar patterns, which we exploit
in a learning algorithm to build rules that
describe a language model for the files.

\para{Translator.}
The translator module first parses the input sample 
dataset (containing both configuration files and system environment
information), and then transforms them to a more structured
and typed intermediate representation.
When we run type inference on a configuration file, 
the type of a variable cannot always be fully determined from 
a single value.
We address this problem 
by introducing so called {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types with their probability distributions. 
We can later use these more structured files
as a training set to learn the rules.

@@

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which needs users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class is looked as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.
\ennan{I do know we are using in some sense templates, but
we should use pattern or some words to persuade we are 
using an implicit ``templates''; otherwise, too similar 
to what EnCore did.}

Although the learner does necessarily rely on templates,
\app still offers a database to contain many templates,
as shown in Figure~\ref{fig-overview}.
Some of these templates are responsible for offering
specific system executional environment information.
It is widely known that any existing learning algorithm cannot
derive rules checking environment violation, \eg,
whether current account is the owner of a certain path.
In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment related configuration errors.

### 2016-05-07 OSDI/motiv.tex
config: more update

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that important
entry was missing in the configuration file. 
We call such a problem as {\em entry missing error}.
Below is a real-world entry missing error example,
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
For example, both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.

>>>>

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that important
entry was missing in the configuration file. 
We call such a problem as {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
the major problems of MySQL failure reports were caused by
entry missing errors.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
For a configuration error reported recently made MySQL
daemon failed to start~\cite{syserror}.
One entry in a MySQL configuration file is written as 
{\tt datadir=/root/appfinder/mysql}, and the type as well as 
format seem to be correct.
However, the problem is this directory should not be
initiated as a root directory, and the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called system environment related configuration error.
Both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.
